Parsing Tweets into Universal Dependencies

### 2017-11-30 paper.tex
.

In the different direction of splitting tokens, UD guidelines also suggest to merge \yicomment{suggest merging?}
{\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
cases. We witnessed a small number of tweets that contain mult-token words
(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
Such tokens only account for 0.067\% and we use the UD
  {\it goeswith} relation to resolve these cases in the dependency annotations.

@@

Another important difference follows from the difference in
tokenization.  As discussed in \S\ref{sec:tok-anno}, UD calls for more
aggressive tokenization than that used by 
\newcite{gimpel-EtAl:2011:ACL-HLT2011} [YICOMMENT: should be OCONNOR's paper? TOKENIZATION?]. In particular, Gimpel et al.~[YICOMMENT: SAME HERE] opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only account for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

>>>>

In the different direction of splitting tokens, UD guidelines also suggest to merge \yicomment{suggest merging?}
{\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
cases. We witnessed a small number of tweets that contain multi-token words
(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
Such tokens only account for 0.067\% and we use the UD
  {\it goeswith} relation to resolve these cases in the dependency annotations.

@@

Another important difference follows from the difference in
tokenization.  As discussed in \S\ref{sec:tok-anno}, UD calls for more
aggressive tokenization than that used by 
\newcite{gimpel-EtAl:2011:ACL-HLT2011} \yicomment{YICOMMENT: should be OCONNOR's paper? TOKENIZATION?}. In particular, Gimpel et al.~\yicomment{SAME HERE} opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only account for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.
